Twists of supersymmetric gauge theories

### 2019-08-16 paper.tex

We call $\cE$ the {\bf space of BV fields}.

@@

Given a classical field theory $(E, Q, \omega, I)$ we denote by
\[S = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
the BV action of the theory.

@@

\begin{dfn}
Let $(E, Q,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras (in differentiable pro-cochain complexes)
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super dg Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
\end{dfn}

@@

@@

\subsubsection{Super Yang--Mills Theory}

@@

@@

\begin{prop} \label{dim_red_SUSY_prop}
The dimensional reduction of a supersymmetric classical field theory on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
\end{prop}

\begin{proof}
 \chris{I think this will be straightforward.}
\end{proof}

@@

In this section, we will consider pairs $(\mf A, \fL)$ consisting of a supersymmetry algebra and an instance of Yang-Mills theory with matter, in one of the following four situations.
\begin{itemize}
 \item Dimension $n=3$ with $\Sigma = S$, the 2-dimensional Dirac representation.
 \item Dimension $n=4$ with $\Sigma = S_+ \oplus S_-$, 4-dimensional Dirac representation.
 \item Dimension $n=6$ with $\Sigma = S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, the 8-dimensional symplectic Weyl representation.
 \item Dimension $n=10$ with $\Sigma = S_+$, the 16-dimensional Weyl representation.
\end{itemize}
We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
\begin{enumerate}
 \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ \chris{define this above}, which is only well-defined on-shell.  In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion \chris{induces a Lie homomorphism on cohomology?}.
 \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
\end{enumerate}
This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.  In particular, we will use the following ``3-$\psi$'s rule'' \chris{see citations in Baez Huerta for more references, which we might include}.  Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.
%We will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.

\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}]
The multilinear map 
\[T \colon \Sigma \otimes \Sigma \otimes \Sigma \otimes \Sigma \to \CC,\]
obtained by symmetrizing the expression $g(\Gamma(\psi_1,\psi_2), \Gamma(\psi_3, \psi_4))$ in the first three variables, is zero.
\end{theorem}

@@

So, we start by discussing the on-shell supersymmetry.  The fermionic part of the supersymmetry algebra is defined by saying that $Q \in \Sigma$ acts infinitesimally by
\[
\begin{pmatrix}
A \\ \lambda
\end{pmatrix}
\mapsto
\begin{pmatrix} A + \delta_Q A \\
\lambda + \delta_Q \lambda
\end{pmatrix}
\]
where 
\begin{align*}
\delta_Q A &= \Gamma(Q,\lambda) \\
\delta_Q \lambda &= \sd F_A Q .
\end{align*}
Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.  We can check that this supersymmetry action does not close off-shell.  Indeed \chris{...}

\chris{heavily edit the below.}
\begin{lemma} \label{10d_onshell_lemma}
Suppose $Q_1, Q_2 \in S_+$ and $(A, \lambda)$ are fields.
The following relations hold:
\begin{itemize}
\item[(1)] \label{10dsusyA} $ [\delta_{Q_1}, \delta_{Q_2}] A = \delta_{[Q_1, Q_2]} A$.
\item[(2)] \label{10dsusyL} $ [\delta_{Q_1}, \delta_{Q_2}] \lambda = \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2$ .
\end{itemize}
Here, the commutator on the left hand side of the equations takes place in the algebra of endomorphisms of the space of fields.
\end{lemma}

\begin{proof}
Both are direct calculations using standard Clifford relations which cite below.
So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
&= \delta_{[Q_1, Q_2]} A,
\end{align*}
where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e. that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.  Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.  Similarly we can calculate, following the calculation in Guillen \cite{Guillen}:
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
\end{align*}
using the fact that 
\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
as in \cite[Theorem 11]{BaezHuerta}.  Making one more simplification using the Clifford relations, we have
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
\end{align*}
\end{proof}

In particular the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".  This calculation suggests introducing a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.  Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
\begin{align*}
\delta^{(2)} \colon S_+ \otimes S_+ \otimes \Gamma(\RR^{10}; \Pi S_-[-1]) &\to \Gamma(\RR^{10}; \Pi S_+) \\
Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
\end{align*}

We'll rewrite this as a local functional in the theory $\fL$ coupled to the $\mc N=(1,0)$ super Lie algebra $\mf A$.

\begin{definition}
The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
where 
\begin{align*}
I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
I^{(2)} (Q_1,Q_2 ; \lambda^*) & = \pm \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
\end{align*}
\end{definition}

\begin{prop}
Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra. The functional
\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL) [-1]\]
satisfies the Maurer-Cartan equation
\begin{equation} 
\label{10d_MC}
(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\} = 0 .
\end{equation}
\end{prop}

\chris{we'll have to see whether we want Poincar\'e or just translation here, probably translation, because then there are no $\d_{\mr{Lie}}I^{(i)}$ terms to worry about.  On the other hand we would like to know that the theories are supersymmetric, not just super-translation invariant.  To include rotations and R-symmetries we need to additionally check that some terms like $\d_{\mr{Lie}}+ \{I_{\mr{rotation}} + I_{\text{R-symmetry}}, I^{(i)}\}$ vanish.}

\begin{proof}
We can filter the complex $\clie^\bu(\mc A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{10d_MC} splits up as
\begin{align}
\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{10d_MC_BV}\\
&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{10d_MC_1}\\
&\quad + \d_{\mr{Lie}} I^{(1)} + \{S_{\mr{BV}}, I^{(2)}\} + \{I_{\mr{Poin}}, I^{(1)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{10d_MC_2}\\
&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{10d_MC_3}\\
&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{10d_MC_4}
\end{align}
Taking these terms one at a time, we first note that the vanishing of \ref{10d_MC_BV} is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, along with the fact that this theory is Poincar\'e invariant \chris{ref some earlier discussion}.  The remaining terms are those involving the action of supersymmetries.

First, the term \ref{10d_MC_1} vanishes by \chris{We've discussed this.  First the $\{I_{\mr{Poin}}, I^{(i)}\}$ terms vanish by Poincar\'e invariance of the interaction terms.  Then \ref{10d_MC_1} is zero by Baez--Huerta.  Term \ref{10d_MC_2} is Lemma \ref{10d_onshell_lemma}. Term \ref{10d_MC_3} vanishes because, first $\d_{\mr{Lie}}I^{(2)} = 0$ since ...not sure right now..., then the remaining term vanishes by the trick where we symmetrize in three spinors.  Finally \ref{10d_MC_4} vanishes because $I^{(2)}$ only involves antifields.}

>>>>

We call $\cE$ the {\bf space of BV fields}.
\chris{before the definition below we should probably define the antibracket $\{,\}$ (in terms of the shifted symplectic structure).}

@@

Given a classical field theory $(E, Q, \omega, I)$ we denote by
\[S_{BV} = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
the BV action of the theory.

@@

\begin{dfn} \label{infinitesimal_action_def}
Let $(E, Q,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras (in differentiable pro-cochain complexes)
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
\end{dfn}

@@

Concretely, an action of a super dg Lie algebra $\fg$ on a classical field theory is given by an element
\[\sum_{k\geq 1} I^{(k)}\in \oloc(E)\otimes \widehat{\sym}^{\geq 1}(\fg^*[-1])\]
which satisfies the Maurer--Cartan equation
\[\{S_{BV}, I^{(k+1)}\} + \d_{CE} I^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I^{(a)}, I^{(b)}\} = 0\]
for every $k\geq 0$.

@@

\subsubsection{Super Yang--Mills Theory} \label{YM_section}

@@

We'll conclude this section with a discussion of the Poincar\'e invariance of classical Yang-Mills theory.

\begin{definition}
The $n$-dimensional {\bf Poincar\'e group} is the group $\mr{ISO}(n) = \SO(n) \ltimes \RR^n$ of isometries of $\RR^n$ with its flat Riemannian metric.  The $n$-dimensional {\bf Poincar\'e algebra} $\mf{iso}(n)$ is the Lie algebra of the Poincar\'e group.
\end{definition}

The $n$-dimensional Poincar\'e algebra acts, in the sense of Definition \ref{infinitesimal_action_def}, on Yang--Mills theory on $\RR^n$ for any choice $\Sigma$ of matter representation.
\chris{define the interaction functional $I_\mr{Poin}$ associated to the Poincar\'e action on Yang-Mills theory.}

\begin{prop} \label{YM_Poincare_invariant_prop}
Yang--Mills theory is \emph{Poincar\'e invariant}.  That is, the classical BV action functional satisfies the Maurer-Cartan equation
\[\{S_{BV}, I_{\mr{Poin}}\} + \d_{CE} I_{\mr{Poin}} + \frac 12 \{I_{\mr{Poin}}, I_{\mr{Poin}}\} = 0.\]
\end{prop}
\begin{proof}
\chris{...}
\end{proof}

@@

\begin{prop} \label{dim_red_SUSY_prop}
The dimensional reduction of a supersymmetric classical field theory $\mf L$ on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory $\mf L'$ on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
\end{prop}

\begin{proof}
 \chris{Here's a proof sketch/outline/idea.} Start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.  There is a cochain map \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}}(\mf{iso}(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf{iso}(m)) \otimes C^\bullet_{\mr{loc}}(p^* \mf L')),\] 
 given by the inclusion of $\mf{iso}(m) \inj \mf{iso}(n)$, and the restriction of a functional to act only those fields which are constant on $(\RR^m)^\perp$.   We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S_{\mr{Poin}}$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S_{\mr{Poin}}) = \mf S'_{\mr{Poin}}$ in $m$-dimensions, i.e a Poincar\'e invariant action functional.

 Now include supertranslations, so start with an $\mf A$-invariant action functional $\mf S$ in $n$-dimensions.  There is a graded linear map $C^\bullet_{\mr{Lie}}(\mf A) \to C^\bullet_{\mr{Lie}}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.  Let's apply the graded linear map \[F \colon (C^\bullet_{\mr{Lie}}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf A') \otimes C^\bullet_{\mr{loc}}(p^*\mf L'))\] to $\mf S$ anyway.  We'll find that $\d F(\mf S) - F \d(\mf S)$ vanishes, because the failure of $F$ and $\d$ to commute involves the action of the translations perpendicular to $\RR^m$, which act trivially on the Poincar\'e invariant theory $\mf L'$.  We can then use the same argument as above. 
\end{proof}

@@

In this section, we will consider pairs $(\mf A, \fL)$ consisting of a supersymmetry algebra and an instance of Yang-Mills theory with matter, in one of the following four situations.
\begin{itemize}
 \item Dimension $n=3$ with $\Sigma = S$, the 2-dimensional Dirac representation.
 \item Dimension $n=4$ with $\Sigma = S_+ \oplus S_-$, 4-dimensional Dirac representation.
 \item Dimension $n=6$ with $\Sigma = S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, the 8-dimensional symplectic Weyl representation.
 \item Dimension $n=10$ with $\Sigma = S_+$, the 16-dimensional Weyl representation.
\end{itemize}

\begin{definition}
In each case we will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.
\end{definition}

We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
\begin{enumerate}
 \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ as discussed in Section \ref{YM_section}, which is only well-defined on-shell.  In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion.
 \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
\end{enumerate}
This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.  In particular, we will use the following ``3-$\psi$'s rule'', discussed in the 10-dimensional case by Schray \cite{Schray} .  Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.

\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}] \label{3_psi_thm}
The multilinear map 
\[T \colon \Sigma \otimes \Sigma \otimes \Sigma \otimes \Sigma \to \CC,\]
obtained by symmetrizing the expression $g(\Gamma(\psi_1,\psi_2), \Gamma(\psi_3, \psi_4))$ in the first three variables, is zero.
\end{theorem}

@@

So, we start by discussing the on-shell supersymmetry.  The fermionic part of the supersymmetry algebra is defined by saying that $Q \in \Sigma$ acts infinitesimally by
\[
\begin{pmatrix}
A \\ \lambda
\end{pmatrix}
\mapsto
\begin{pmatrix} A + \delta_Q A \\
\lambda + \delta_Q \lambda
\end{pmatrix}
\]
where 
\begin{align*}
\delta_Q A &= \Gamma(Q,\lambda) \\
\delta_Q \lambda &= \sd F_A Q .
\end{align*}
Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.  We can check that this supersymmetry action does not close off-shell.

\begin{lemma} \label{onshell_action_lemma}
Suppose $Q_1, Q_2 \in \Sigma$ and $(A, \lambda)$ are super Yang-Mills fields.
The following relations hold:
\begin{itemize}
\item[(1)] \label{10dsusyA} $ [\delta_{Q_1}, \delta_{Q_2}] A = \delta_{[Q_1, Q_2]} A$.
\item[(2)] \label{10dsusyL} $ [\delta_{Q_1}, \delta_{Q_2}] \lambda = \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2$ .
\end{itemize}
Here, the commutator on the left hand side of the equations takes place in the algebra of endomorphisms of the space of fields.
\end{lemma}

\begin{proof}
\chris{I'm leaving this for now, but Pavel wanted to rewrite this coordinate freely.}
Both are direct calculations using standard Clifford relations which cite below.
So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
&= \delta_{[Q_1, Q_2]} A,
\end{align*}
where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e. that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.  Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.  Similarly we can calculate, (as in \cite{Guillen}):
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
\end{align*}
using the fact that 
\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
as in Theorem \ref{3_psi_thm}.  Making one more simplification using the Clifford relations, we have
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
\end{align*}
\end{proof}

In particular the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".  This calculation suggests introducing a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.  Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
\begin{align*}
\delta^{(2)} \colon \Sigma \otimes \Sigma \otimes \Gamma(\RR^{n}; \Pi \wt \Sigma[-1]) &\to \Gamma(\RR^{n}; \Pi \Sigma) \\
Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
\end{align*}

We'll rewrite this as a local functional in the theory $\fL$ coupled to the supersymmetry Lie algebra $\mf A$.

\begin{definition}
The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
where 
\begin{align*}
I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
I^{(2)} (Q_1,Q_2 ; \lambda^*) & =  \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
\end{align*}
\end{definition}

We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.
\begin{lemma} \label{onshell_interaction_lemma}
The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
\[\{I^{(1)},I^{(1)}\} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
\end{lemma}

\begin{proof}
This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
\begin{align*}
\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_{Q_1} A\> + \<\lambda^*, \delta_{Q_1} \lambda\>, \<A^* , \delta_{Q_2} A\> + \<\lambda^*, \delta_{Q_2} \lambda\> \} \\
&= 2(\langle A^*, [\delta_{Q_1}, \delta_{Q_2}] A \rangle + \langle \lambda^*, [\delta_{Q_1}, \delta_{Q_2}] \lambda \rangle) \\
 &= 2(\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + \langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle  - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_1, \sd \dd \lambda)Q_2 - \frac 12(Q_2, \sd \dd \lambda)Q_1) \\
 &= 2\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + 2\langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
 &=
\end{align*}
Here we applied Lemma \ref{onshell_action_lemma} on the third line, and on the last line we used the 
\chris{What about that $[Q_1,Q_2]$ term?  It looks like the interaction $I_{\mr{trans}}$ associated to the translation $[Q_1,Q_2]$.}
\end{proof}

The functionals $I^{(1)}$ and $I^{(2)}$ are also rotation invariant, in the following sense.
\begin{lemma} \label{SUSY_rotation_invariance_lemma}
Let $I_{\mr{Poin}}$ be the interaction associated to the action of $\mf{iso}(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.  The functionals $I^{(1)}$ and $I^{(2)}$ are Poincar\'e invariant, meaning that
\begin{equation}\label{rot_invariance_eqn}
 \d_{\mr{Lie}} I^{(i)} = - \{I_{\mr{Poin}}, I^{(i)}\},
\end{equation}
for $i=1,2$.
\end{lemma}

\begin{proof}
First, note that only the action of $\so(n)$ contributes to the two terms in the expression \ref{rot_invariance_eqn}, since the Lie bracket between a supertranslation and an ordinary translation is always zero.  If we then consider the space $\Sigma$ of supertranslations as an $\so(n)$-module, 
\chris{...}
\end{proof}

Now that we've defined the supersymmetry action, we can prove the main theorem of this section: that minimal super Yang-Mills theory in dimensions $n=3,4,6$ and 10 is, indeed, a supersymmetric classical field theory.

\begin{theorem} \label{SUSY_YM_theorem}
Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra. The functional
\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]\]
satisfies the Maurer-Cartan equation
\begin{equation} 
\label{nd_MC}
(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\}) = 0 .
\end{equation}
\end{theorem}
